Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-11-08 2017-EUROPAR/Gamification/paper.tex
Adds bib for socio-technical systems

\keywords{Distributed Evolutionary Algorithms, Volunteer Computing}
\end{abstract}

@@

There are several open issues in the research regarding the application of volunteer computing techniques to the development of distributed evolutionary algorithms of which the most important is approaching the problem as a socio-technical system \cite{vespignani2009predicting}. which integrates user decisions and behavioral patterns in the model; this
includes trying to optimize the number of users in a particular
experiment. The challenge is to design a system that, whatever the
number of users available to perform the experiment, is able to
maximize their contribution to the evolutionary algorithm. One obvious
way of achieving that is trying to find as many users as possible. But
another approach, and the one that we will be following in this paper, is
to delve into the socio-technical nature of the system, using
gamification techniques to improve the amount of time every user will lend to the system. Gamification has to include some way of user authentification,
which is a hurdle that might take users away; however, the open design
of the system we use means that we can actually mix anonymous-non
gamified and authentified-gamified users, with only the small overhead
of adding the gamification mechanism.

@@

The fact that gamification actually work highlights the social nature of volunteer computing systems, piling on the fact that successful {\em social clouds} must embed games and other social mechanisms to enhance participation. That is why future lines of work will look for intermediate ways of including
gamification without registration, as well as some ways of making the user increase control over the algorithm that would go beyond simply staying for longer or leaving the page. Since it is a sociotechnical system, including social features in it and studying emerging social networks might be an interesting line of work too.

@@

\section{Conclusions}
\label{sec:conclusions}

>>>>

\keywords{Distributed Evolutionary Algorithms, Volunteer Computing,
  Socio-Technical Systems}
\end{abstract}

@@

There are several open issues in the research regarding the
application of volunteer computing techniques to the development of
distributed evolutionary algorithms of which the most important is
approaching the problem as a socio-technical system
\cite{vespignani2009predicting,merelo2015designing}. which integrates
user decisions and behavioral patterns in the model; this 
includes trying to optimize the number of users in a particular
experiment. The challenge is to design a system that, whatever the
number of users available to perform the experiment, is able to
maximize their contribution to the evolutionary algorithm. One obvious
way of achieving that is trying to find as many users as possible. But
another approach, and the one that we will be following in this paper, is
to delve into the socio-technical nature of the system, using
gamification techniques to improve the amount of time every user will
lend to the system. Gamification has to include some way of user authentification,
which is a hurdle that might take users away; however, the open design
of the system we use means that we can actually mix anonymous-non
gamified and authentified-gamified users, with only the small overhead
of adding the gamification mechanism.

@@

The fact that gamification actually work highlights the social nature of volunteer computing systems, piling on the fact that successful {\em social clouds} must embed games and other social mechanisms to enhance participation. That is why future lines of work will look for intermediate ways of including
gamification without registration, as well as some ways of making the
user increase control over the algorithm that would go beyond simply
staying for longer or leaving the page. Since it is a sociotechnical
system, including social features in it and studying emerging social
networks is an interesting line of work too.

@@
